### 2021-09-16 paper/output/document/paper31.tex
finished kroy FUL tests

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will present two formulations of the categorical imperative. In Section \ref{sec:naive}, I will 
consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
tests that Isabelle can carry out. In Section \ref{sec:kroy}, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
the first two formulations of the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formulation of the Formula of Universal Law \label{sec:naive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the formula of universal law, which 
is to will only those maxims that you would simultaneously will universalized. The universalizability 
test creates negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
it is prohibited. In order to appropriately formalize this, we need some notion of permissibility.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlpermissable{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}P\ A{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{An act $A$ is permissible if its negation is not obligated. For example, buying a red folder is 
permissible because I am not required to refrain from buying a red folder.%
}%
\begin{isamarkuptext}%
This naive formalization will require very little additional logical machinery, but more complex
formalizations may require additional logic concepts.

@@

%:%66=22%:%
%:%67=22%:%
%:%68=23%:%
%:%70=24%:%
%:%71=25%:%
%:%74=27%:%
%:%75=28%:%
%:%76=29%:%
%:%77=30%:%
%:%78=31%:%
%:%79=32%:%
%:%80=33%:%
%:%81=34%:%
%:%83=36%:%
%:%84=36%:%
%:%85=37%:%
%:%87=39%:%
%:%88=40%:%
%:%89=41%:%
%:%90=42%:%
%:%91=43%:%
%:%92=44%:%
%:%93=45%:%
%:%94=46%:%
%:%95=47%:%
%:%96=48%:%
%:%97=49%:%
%:%98=50%:%
%:%100=53%:%
%:%101=53%:%
%:%102=53%:%
%:%104=53%:%
%:%108=53%:%
%:%109=53%:%
%:%111=54%:%
%:%112=55%:%
%:%113=56%:%
%:%114=56%:%
%:%116=57%:%
%:%117=58%:%
%:%118=59%:%
%:%119=59%:%
%:%186=105%:%
%:%198=107%:%
%:%199=108%:%
%:%200=109%:%
%:%201=110%:%
%:%203=112%:%
%:%204=112%:%
%:%205=113%:%
%:%206=113%:%
%:%218=121%:%
%:%221=122%:%
%:%222=122%:%
%:%224=123%:%
%:%225=124%:%
%:%226=125%:%
%:%227=126%:%
%:%228=126%:%
%:%229=127%:%
%:%230=128%:%
%:%231=128%:%
%:%232=129%:%
%:%235=130%:%
%:%239=130%:%
%:%240=130%:%
%:%242=131%:%
%:%243=132%:%
%:%253=134%:%
%:%254=135%:%
%:%255=136%:%
%:%259=138%:%
%:%261=140%:%
%:%262=140%:%
%:%263=141%:%
%:%264=141%:%
%:%265=142%:%
%:%266=142%:%
%:%268=143%:%
%:%269=143%:%
%:%270=144%:%
%:%271=145%:%
%:%272=145%:%
%:%274=147%:%
%:%275=148%:%
%:%276=149%:%
%:%277=150%:%
%:%279=152%:%
%:%280=152%:%
%:%281=153%:%
%:%282=154%:%
%:%283=155%:%
%:%284=155%:%
%:%287=156%:%
%:%291=156%:%
%:%292=156%:%
%:%294=157%:%
%:%295=158%:%
%:%296=159%:%
%:%297=160%:%
%:%298=160%:%
%:%300=161%:%
%:%301=162%:%
%:%302=163%:%
%:%303=164%:%
%:%304=165%:%
%:%305=165%:%
%:%307=166%:%
%:%308=167%:%
%:%318=169%:%
%:%319=170%:%
%:%320=171%:%
%:%321=172%:%
%:%322=173%:%
%:%323=174%:%
%:%324=175%:%
%:%325=176%:%
%:%327=178%:%
%:%328=178%:%
%:%329=179%:%
%:%330=180%:%
%:%331=181%:%
%:%332=181%:%
%:%334=181%:%
%:%338=181%:%
%:%339=181%:%
%:%341=182%:%
%:%342=183%:%
%:%343=184%:%
%:%344=185%:%
%:%345=186%:%
%:%346=187%:%
%:%356=189%:%
%:%357=190%:%
%:%358=191%:%
%:%359=192%:%
%:%360=193%:%
%:%361=194%:%
%:%370=196%:%

@@

%:%383=199%:%
%:%384=200%:%
%:%385=201%:%
%:%386=202%:%
%:%387=203%:%
%:%388=204%:%
%:%389=205%:%
%:%390=206%:%
%:%391=207%:%
%:%392=208%:%
%:%393=209%:%
%:%395=210%:%
%:%396=210%:%
%:%397=211%:%
%:%398=212%:%
%:%399=212%:%
%:%401=212%:%
%:%405=212%:%
%:%406=212%:%
%:%408=213%:%
%:%409=214%:%
%:%410=215%:%
%:%411=216%:%
%:%412=216%:%
%:%414=217%:%
%:%415=218%:%
%:%416=219%:%
%:%417=219%:%
%:%419=220%:%
%:%420=221%:%
%:%428=221%:%
%:%429=222%:%
%:%430=223%:%
%:%431=223%:%
%:%432=224%:%
%:%433=225%:%
%:%434=226%:%
%:%435=226%:%
%:%437=226%:%
%:%441=226%:%
%:%442=226%:%
%:%444=227%:%
%:%445=228%:%
%:%446=229%:%
%:%447=230%:%
%:%448=230%:%
%:%450=231%:%
%:%451=232%:%
%:%452=233%:%
%:%462=235%:%
%:%463=236%:%
%:%465=238%:%
%:%466=238%:%
%:%467=239%:%
%:%468=240%:%
%:%469=241%:%
%:%470=241%:%
%:%472=241%:%
%:%476=241%:%
%:%477=241%:%
%:%479=242%:%
%:%480=243%:%
%:%481=244%:%
%:%482=245%:%
%:%483=245%:%
%:%485=246%:%
%:%495=248%:%
%:%499=250%:%
%:%500=251%:%
%:%501=252%:%
%:%502=253%:%
%:%504=255%:%
%:%505=255%:%
%:%506=256%:%
%:%507=257%:%
%:%508=258%:%
%:%509=258%:%
%:%511=258%:%
%:%515=258%:%
%:%516=258%:%
%:%518=259%:%
%:%519=260%:%
%:%520=261%:%
%:%521=262%:%
%:%522=262%:%
%:%524=263%:%
%:%534=265%:%
%:%535=266%:%
%:%536=267%:%
%:%538=269%:%
%:%539=269%:%
%:%540=270%:%
%:%541=271%:%
%:%542=272%:%
%:%543=272%:%
%:%545=272%:%
%:%549=272%:%
%:%550=272%:%
%:%552=273%:%
%:%553=274%:%
%:%554=275%:%
%:%555=275%:%
%:%557=276%:%
%:%567=278%:%
%:%568=279%:%
%:%569=280%:%
%:%571=282%:%
%:%572=282%:%
%:%573=283%:%
%:%574=284%:%
%:%575=285%:%
%:%576=286%:%
%:%577=287%:%
%:%578=287%:%
%:%585=288%:%
%:%586=288%:%
%:%587=289%:%
%:%588=289%:%
%:%589=290%:%
%:%590=290%:%
%:%591=291%:%
%:%592=291%:%
%:%593=291%:%
%:%594=291%:%
%:%596=292%:%
%:%597=293%:%
%:%598=293%:%
%:%599=294%:%
%:%600=294%:%
%:%601=294%:%
%:%603=295%:%
%:%604=296%:%
%:%605=297%:%
%:%606=298%:%
%:%607=299%:%
%:%608=299%:%
%:%610=300%:%
%:%620=302%:%
%:%621=303%:%
%:%622=304%:%
%:%623=305%:%
%:%624=306%:%
%:%626=308%:%
%:%627=308%:%
%:%628=309%:%
%:%629=310%:%
%:%630=311%:%
%:%631=311%:%
%:%633=311%:%
%:%637=311%:%
%:%638=311%:%
%:%640=312%:%
%:%641=313%:%
%:%642=314%:%
%:%643=315%:%
%:%644=316%:%
%:%654=318%:%
%:%655=319%:%
%:%659=321%:%
%:%663=323%:%
%:%664=324%:%
%:%665=325%:%
%:%667=327%:%
%:%668=327%:%
%:%669=328%:%
%:%672=329%:%
%:%676=329%:%
%:%677=329%:%
%:%679=330%:%
%:%680=330%:%
%:%682=331%:%
%:%683=332%:%
%:%684=333%:%
%:%685=334%:%
%:%686=335%:%
%:%696=337%:%
%:%697=338%:%
%:%698=339%:%
%:%699=340%:%
%:%701=342%:%
%:%702=342%:%
%:%703=343%:%
%:%706=344%:%
%:%710=344%:%
%:%711=344%:%
%:%712=344%:%
%:%714=345%:%
%:%715=345%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{paper{\isadigit{3}}{\isadigit{1}}}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Prior Formalizations of The Categorical Imperative%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this section, I will present two formulations of the categorical imperative. In Section \ref{sec:naive}, I will 
consider a simple, naive formulation of the formula of universal law. This formulation is, as I will 
show, clearly not a good ethical rule. The purpose of this section is to explore the kinds of ethical
tests that Isabelle can carry out. In Section \ref{sec:kroy}, I will explore Moshe Kroy's \cite{kroy} partial formalization of 
the first two formulations of the categorical imperative.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Naive Formalization of the Formula of Universal Law \label{sec:naive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
This section presents a simple and intuitive formalization of the formula of universal law, which 
is to will only those maxims that you would simultaneously will universalized. The universalizability 
test creates negative obligations: if a maxim passes the universalizability test, it is permissible. Else,
it is prohibited.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Formalization \label{sec:naive_form}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In order to appropriately formalize the categorical imperative, we to define the notion of permissibility.%
\end{isamarkuptext}\isamarkuptrue%
\isacommand{abbreviation}\isamarkupfalse%
\ ddlpermissable{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}t{\isasymRightarrow}t{\isachardoublequoteclose}\ {\isacharparenleft}{\isachardoublequoteopen}P{\isacharunderscore}{\isachardoublequoteclose}{\isacharparenright}\isanewline
\ \ \isakeyword{where}\ {\isachardoublequoteopen}{\isacharparenleft}P\ A{\isacharparenright}\ {\isasymequiv}\ {\isacharparenleft}\isactrlbold {\isasymnot}{\isacharparenleft}O\ {\isacharbraceleft}\isactrlbold {\isasymnot}A{\isacharbraceright}{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}\isanewline
%
\isamarkupcmt{An act $A$ is permissible if its negation is not obligated. For example, buying a red folder is 
permissible because I am not required to refrain from buying a red folder.%
}%
\begin{isamarkuptext}%
This naive formalization will require very little additional logical machinery, but more complex
formalizations may require additional logic concepts.

@@

%:%73=22%:%
%:%85=24%:%
%:%87=26%:%
%:%88=26%:%
%:%89=27%:%
%:%91=28%:%
%:%92=29%:%
%:%95=31%:%
%:%96=32%:%
%:%97=33%:%
%:%98=34%:%
%:%99=35%:%
%:%100=36%:%
%:%101=37%:%
%:%102=38%:%
%:%104=40%:%
%:%105=40%:%
%:%106=41%:%
%:%108=43%:%
%:%109=44%:%
%:%110=45%:%
%:%111=46%:%
%:%112=47%:%
%:%113=48%:%
%:%114=49%:%
%:%115=50%:%
%:%116=51%:%
%:%117=52%:%
%:%118=53%:%
%:%119=54%:%
%:%121=57%:%
%:%122=57%:%
%:%123=57%:%
%:%125=57%:%
%:%129=57%:%
%:%130=57%:%
%:%132=58%:%
%:%133=59%:%
%:%134=60%:%
%:%135=60%:%
%:%137=61%:%
%:%138=62%:%
%:%139=63%:%
%:%140=63%:%
%:%207=109%:%
%:%219=111%:%
%:%220=112%:%
%:%221=113%:%
%:%222=114%:%
%:%224=116%:%
%:%225=116%:%
%:%226=117%:%
%:%227=117%:%
%:%239=125%:%
%:%242=126%:%
%:%243=126%:%
%:%245=127%:%
%:%246=128%:%
%:%247=129%:%
%:%248=130%:%
%:%249=130%:%
%:%250=131%:%
%:%251=132%:%
%:%252=132%:%
%:%253=133%:%
%:%256=134%:%
%:%260=134%:%
%:%261=134%:%
%:%263=135%:%
%:%264=136%:%
%:%274=138%:%
%:%275=139%:%
%:%276=140%:%
%:%280=142%:%
%:%282=144%:%
%:%283=144%:%
%:%284=145%:%
%:%285=145%:%
%:%286=146%:%
%:%287=146%:%
%:%289=147%:%
%:%290=147%:%
%:%291=148%:%
%:%292=149%:%
%:%293=149%:%
%:%295=151%:%
%:%296=152%:%
%:%297=153%:%
%:%298=154%:%
%:%300=156%:%
%:%301=156%:%
%:%302=157%:%
%:%303=158%:%
%:%304=159%:%
%:%305=159%:%
%:%308=160%:%
%:%312=160%:%
%:%313=160%:%
%:%315=161%:%
%:%316=162%:%
%:%317=163%:%
%:%318=164%:%
%:%319=164%:%
%:%321=165%:%
%:%322=166%:%
%:%323=167%:%
%:%324=168%:%
%:%325=169%:%
%:%326=169%:%
%:%328=170%:%
%:%329=171%:%
%:%339=173%:%
%:%340=174%:%
%:%341=175%:%
%:%342=176%:%
%:%343=177%:%
%:%344=178%:%
%:%345=179%:%
%:%346=180%:%
%:%348=182%:%
%:%349=182%:%
%:%350=183%:%
%:%351=184%:%
%:%352=185%:%
%:%353=185%:%
%:%355=185%:%
%:%359=185%:%
%:%360=185%:%
%:%362=186%:%
%:%363=187%:%
%:%364=188%:%
%:%365=189%:%
%:%366=190%:%
%:%367=191%:%
%:%377=193%:%
%:%378=194%:%
%:%379=195%:%
%:%380=196%:%
%:%381=197%:%

@@

%:%391=200%:%
%:%403=202%:%
%:%404=203%:%
%:%405=204%:%
%:%406=205%:%
%:%407=206%:%
%:%408=207%:%
%:%409=208%:%
%:%410=209%:%
%:%411=210%:%
%:%412=211%:%
%:%413=212%:%
%:%414=213%:%
%:%416=214%:%
%:%417=214%:%
%:%418=215%:%
%:%419=216%:%
%:%420=216%:%
%:%422=216%:%
%:%426=216%:%
%:%427=216%:%
%:%429=217%:%
%:%430=218%:%
%:%431=219%:%
%:%432=220%:%
%:%433=220%:%
%:%435=221%:%
%:%436=222%:%
%:%437=223%:%
%:%438=223%:%
%:%440=224%:%
%:%441=225%:%
%:%449=225%:%
%:%450=226%:%
%:%451=227%:%
%:%452=227%:%
%:%453=228%:%
%:%454=229%:%
%:%455=230%:%
%:%456=230%:%
%:%458=230%:%
%:%462=230%:%
%:%463=230%:%
%:%465=231%:%
%:%466=232%:%
%:%467=233%:%
%:%468=234%:%
%:%469=234%:%
%:%471=235%:%
%:%472=236%:%
%:%473=237%:%
%:%483=239%:%
%:%484=240%:%
%:%486=242%:%
%:%487=242%:%
%:%488=243%:%
%:%489=244%:%
%:%490=245%:%
%:%491=245%:%
%:%493=245%:%
%:%497=245%:%
%:%498=245%:%
%:%500=246%:%
%:%501=247%:%
%:%502=248%:%
%:%503=249%:%
%:%504=249%:%
%:%506=250%:%
%:%516=252%:%
%:%520=254%:%
%:%521=255%:%
%:%522=256%:%
%:%523=257%:%
%:%525=259%:%
%:%526=259%:%
%:%527=260%:%
%:%528=261%:%
%:%529=262%:%
%:%530=262%:%
%:%532=262%:%
%:%536=262%:%
%:%537=262%:%
%:%539=263%:%
%:%540=264%:%
%:%541=265%:%
%:%542=266%:%
%:%543=266%:%
%:%545=267%:%
%:%555=269%:%
%:%556=270%:%
%:%557=271%:%
%:%559=273%:%
%:%560=273%:%
%:%561=274%:%
%:%562=275%:%
%:%563=276%:%
%:%564=276%:%
%:%566=276%:%
%:%570=276%:%
%:%571=276%:%
%:%573=277%:%
%:%574=278%:%
%:%575=279%:%
%:%576=279%:%
%:%578=280%:%
%:%588=282%:%
%:%589=283%:%
%:%590=284%:%
%:%592=286%:%
%:%593=286%:%
%:%594=287%:%
%:%595=288%:%
%:%596=289%:%
%:%597=290%:%
%:%598=291%:%
%:%599=291%:%
%:%606=292%:%
%:%607=292%:%
%:%608=293%:%
%:%609=293%:%
%:%610=294%:%
%:%611=294%:%
%:%612=295%:%
%:%613=295%:%
%:%614=295%:%
%:%615=295%:%
%:%617=296%:%
%:%618=297%:%
%:%619=297%:%
%:%620=298%:%
%:%621=298%:%
%:%622=298%:%
%:%624=299%:%
%:%625=300%:%
%:%626=301%:%
%:%627=302%:%
%:%628=303%:%
%:%629=303%:%
%:%631=304%:%
%:%641=306%:%
%:%642=307%:%
%:%643=308%:%
%:%644=309%:%
%:%645=310%:%
%:%647=312%:%
%:%648=312%:%
%:%649=313%:%
%:%650=314%:%
%:%651=315%:%
%:%652=315%:%
%:%654=315%:%
%:%658=315%:%
%:%659=315%:%
%:%661=316%:%
%:%662=317%:%
%:%663=318%:%
%:%664=319%:%
%:%665=320%:%
%:%675=322%:%
%:%676=323%:%
%:%680=325%:%
%:%684=327%:%
%:%685=328%:%
%:%686=329%:%
%:%688=331%:%
%:%689=331%:%
%:%690=332%:%
%:%693=333%:%
%:%697=333%:%
%:%698=333%:%
%:%700=334%:%
%:%701=334%:%
%:%703=335%:%
%:%704=336%:%
%:%705=337%:%
%:%706=338%:%
%:%707=339%:%
%:%717=341%:%
%:%718=342%:%
%:%719=343%:%
%:%720=344%:%
%:%722=346%:%
%:%723=346%:%
%:%724=347%:%
%:%727=348%:%
%:%731=348%:%
%:%732=348%:%
%:%733=348%:%
%:%735=349%:%
%:%736=349%:%
